### 2011-08-01 doc/theses/svirec/kap4.tex
thesis fixing

After creating the RW-XML tree from input XML data, a set of tree tuples (defined in Definition r\ref{treeTuple}) is constructed. Since the set $paths(D)$, containing all possible paths defined in DTD $D$, can be infinite (DTD can define recursive structure of elements), the actual content of $paths(D)$ is modified to reflect the current structure of the RW-XML tree. Since definition of a tree tuple says that answer to the path $p$ contains at most one element, our modification of $paths(D)$ has no effect on constructing tree tuples if a DTD defines some optional path which is not defined for the RW-XML tree $RWXT$ (the set $p(RWXT)$ is empty).

@@

\begin{define}[Repair Candidate Cost]
Being given an RW-XML tree $RXT$ and a repair candidate $R$, we define the cost of $R$ as:
$$cost(R) = \sum_{u \in Modified_\delta(R)} \omega(u) + \sum_{v \in Modified_\varrho(R)} \omega(v) \cdot k,$$
where $k$ is the priority of repairing the candidate by modifying the node value in constrast to marking it unreliable.\qed
\end{define}

>>>>

After creating the RW-XML tree from input XML data, a set of tree tuples (defined in Definition \ref{treeTuple}) is constructed. Since the set $paths(D)$, containing all possible paths defined in DTD $D$, can be infinite (DTD can define recursive structure of elements), the actual content of $paths(D)$ is modified to reflect the current structure of the RW-XML tree. Since definition of a tree tuple says that answer to the path $p$ contains at most one element, our modification of $paths(D)$ has no effect on constructing tree tuples if a DTD defines some optional path which is not defined for the RW-XML tree $RWXT$ (the set $p(RWXT)$ is empty).

@@

\begin{define}[Repair Candidate Cost]
Being given an RW-XML tree $RXT$ and a repair candidate $R$, we define the {\sl cost} of $R$ as:
$$cost(R) = \sum_{u \in Modified_\delta(R)} \omega(u) + \sum_{v \in Modified_\varrho(R)} \omega(v) \cdot k,$$
where $k$ is the priority of repairing the candidate by modifying the node value in constrast to marking it unreliable.\qed
\end{define}
